---
title: "Advanced Data Structures in R"
author: "Vivekanandan Srinivasan"
date: "11/26/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating Simple Dataframe

```{r}
x <- 10:1
y <- -4:5
q <- c("Hockey", "Football", "Baseball", "Curling", "Rugby",      "Lacrosse", "Basketball", "Tennis", "Cricket", "Soccer")
theDF <- data.frame(x, y, q)
theDF

```

## Creating simple dataframe with custom column names

```{r}
theDF <- data.frame(First=x, Second=y, Sport=q)
theDF
```

## Finding dimensions of the dataframe

```{r}
nrow(theDF)
ncol(theDF)
dim(theDF)
```

```{r}
names(theDF)
```

```{r}
rownames(theDF)
```

## Printing first few rows

```{r}
head(theDF)
```


```{r}
theDF$Sport
```

## Accessing Dataframes

```{r}
theDF[3, 2]
```

```{r}
theDF[c(3, 5), 2:3]
```

## Creating Dummy Variables

```{r}
model.matrix(~	theDF$Sport	-	1)

```

## Creating Lists

```{r}
list(1, 2, 3)
```


```{r}
list(theDF, 1:10)
```

## Creating named lists

```{r}
a <- list(TheDataFrame=theDF, TheVector=1:10)
a
```

```{r}
a[["TheDataFrame"]]

```

## Addding element to list

```{r}
length(a)

## adding new element to list
a[[3]] <- "4"
length(a)
```

## Creating matrices

```{r}
# create a 5x2 matrix
A <- matrix(1:10, nrow=5)
# create another 5x2 matrix
B <- matrix(21:30, nrow=5)
# create another 2x5 matrix
C <- matrix(21:40, nrow=2)
```

```{r}
A
B
C
```

## Matrix multiplication

```{r}
A	%*%	t(B)
```

## Assigning row and colnames

```{r}
rownames(A) <- c("1st", "2nd", "3rd", "4th", "5th")
colnames(C) <- LETTERS[1:10]
A %*% C
```


## Arrays

```{r}
 theArray <- array(1:12,	dim=c(2,	3,	2))
theArray
```

## Accessing different dimension in array

```{r}
theArray[1,	,	]
theArray[1,	,	1]
theArray[,	,	1]

```

