---
title: "Model Diagnostics and Selection"
author: "Vivekanandan Srinivasan"
date: "12/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Building Regression Model

```{r}
housing	<- read.table("../data/housing.csv",sep	=	",",	header	=	TRUE,stringsAsFactors	=	FALSE)
names(housing)	<- c("Neighborhood",	"Class",	"Units",	"YearBuilt","SqFt",	"Income",	"IncomePerSqFt",	"Expense",
                    "ExpensePerSqFt",	"NetIncome",	"Value","ValuePerSqFt",	"Boro")
housing <- housing[housing$Units <   1000, ]
house1	<- lm(ValuePerSqFt	~	Units	+	SqFt	+	Boro,	data=housing)
summary(house1)

```

## Visualizing Coefficient Values

```{r}
library(coefplot)
coefplot(house1)
```



```{r}
library(ggplot2)
#	see	what	a	fortified	lm	model	looks	like
head(fortify(house1))
```


## Constructing Residual Plots

```{r}
ggplot(aes(x=.fitted,	y=.resid),	data	=	house1)	+
  geom_point()	+
  geom_hline(yintercept	=	0)	+
  geom_smooth(se	=	FALSE)	+
  labs(x="Fitted	Values",	y="Residuals")
```

## Residual plot with boro separated

```{r}
ggplot(aes(x=.fitted,	y=.resid),	data	=	house1)	+
  geom_point()	+
  geom_hline(yintercept	=	0)	+
  geom_smooth(se	=	FALSE)	+
  labs(x="Fitted	Values",	y="Residuals") +
  geom_point(aes(color=Boro))
```

## Q-Q Plot

```{r}
ggplot(house1,	aes(sample=.stdresid))	+	stat_qq()	+	geom_abline()
```


## Histogram of residuals

```{r}
ggplot(house1,	aes(x=.resid))	+	geom_histogram()
```

## Fitting different models on housing data

```{r}
house2	<- lm(ValuePerSqFt	~	Units	*	SqFt	+	Boro,	data=housing)
house3	<- lm(ValuePerSqFt	~	Units	+	SqFt	*	Boro	+	Class,data=housing)
house4	<- lm(ValuePerSqFt	~	Units	+	SqFt	*	Boro	+	SqFt*Class,data=housing)
house5	<- lm(ValuePerSqFt	~	Boro	+	Class,	data=housing)
```

##  Building coef plots for multiple models

```{r}
multiplot(house1,	house2,	house3,	house4,	house5,	pointSize=2)
```

## Finding Best Model using ANOVA

```{r}
anova(house1,	house2,	house3,	house4,	house5)

```

## Model Selection Using AIC and BIC

```{r}
AIC(house1, house2, house3, house4, house5)
BIC(house1, house2, house3, house4, house5)
```


## Model selection using cross validation

```{r}
library(boot)
#refit	house1	using	glm	instead	of	lm
houseG1	<- glm(ValuePerSqFt	~	Units	+	SqFt	+	Boro,data=housing,	family=gaussian(link="identity"))

#	ensure	it	gives	the	same	results	as	lm
identical(coef(house1),	coef(houseG1))
```

```{r}
houseCV1	<- cv.glm(housing,	houseG1,	K=5)
houseCV1$delta


```

## Building and cross validating multiple models

```{r}
houseG2	<- glm(ValuePerSqFt	~	Units	*	SqFt	+	Boro,	data=housing)
houseG3	<- glm(ValuePerSqFt	~	Units	+	SqFt	*	Boro	+	Class,data=housing)
houseG4	<- glm(ValuePerSqFt	~	Units	+	SqFt	*	Boro	+	SqFt*Class,data=housing)
houseG5	<- glm(ValuePerSqFt	~	Boro	+	Class,	data=housing)

#	run	cross-validation
houseCV2	<- cv.glm(housing,	houseG2,	K=5)
houseCV3	<- cv.glm(housing,	houseG3,	K=5)
houseCV4	<- cv.glm(housing,	houseG4,	K=5)
houseCV5	<- cv.glm(housing,	houseG5,	K=5)

## Creating a dataframe of model Error values and adding model	name
cvResults	<- as.data.frame(rbind(houseCV1$delta,	houseCV2$delta,	houseCV3$delta,	houseCV4$delta,houseCV5$delta))
names(cvResults)	<- c("Error",	"Adjusted.Error")
cvResults$Model	<- sprintf("houseG%s",	1:5)

cvResults
```


## Visualizing model selection methods

```{r}
# measure with ANOVA
cvANOVA	<-anova(houseG1,	houseG2,	houseG3,	houseG4,	houseG5)
cvResults$ANOVA	<-	cvANOVA$`Resid. Dev`

#	measure	with	AIC
cvResults$AIC	<- AIC(houseG1,	houseG2,	houseG3,	houseG4,	houseG5)$AIC

#	make	the	data.frame	suitable	for	plotting
library(reshape2)
cvMelt	<- melt(cvResults,	id.vars="Model",	variable.name="Measure",value.name="Value")

# Plotting Results
ggplot(cvMelt,	aes(x=Model,	y=Value))	+
  geom_line(aes(group=Measure,	color=Measure))	+
  facet_wrap(~Measure,	scales="free_y")	+
  theme(axis.text.x=element_text(angle=90,	vjust=.5))	+
  guides(color=FALSE)

```


