---
title: "Multiple Linear Regression In R"
author: "Vivekanandan Srinivasan"
date: "12/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
housing	<- read.table("../data/housing.csv",
                      sep	=	",",	header	=	TRUE,
                      stringsAsFactors	=	FALSE)
head(housing)
```

## Renaming Columns

```{r}
names(housing)	<- c("Neighborhood",	"Class",	"Units",	"YearBuilt",
                    "SqFt",	"Income",	"IncomePerSqFt",	"Expense",
                    "ExpensePerSqFt",	"NetIncome",	"Value",
                    "ValuePerSqFt",	"Boro")
head(housing)
```

## Visualizing response variable

```{r}
require(ggplot2)
ggplot(housing,	aes(x=ValuePerSqFt))	+ geom_histogram(binwidth=10)	+	labs(x="Value	per	Square	Foot")
```

## Understanding the response variable for different Boro

```{r}
require(gridExtra)
p1 <- ggplot(housing,	aes(x=ValuePerSqFt,	fill=Boro))	+ geom_histogram(binwidth=10)	+	
        labs(x="Value	per	Square	Foot") + theme(axis.text.x = element_text(angle = 90))
p2 <- ggplot(housing,	aes(x=ValuePerSqFt,	fill=Boro))	+ geom_histogram(binwidth=10)	+	
        labs (x="Value	per	Square	Foot")	+      facet_wrap(~Boro) + theme(axis.text.x = element_text(angle = 90))
grid.arrange(p1, p2, nrow = 1,widths=c(3, 5))
```

## Visualizing Predictor variables 

```{r}
p3 <- ggplot(housing,	aes(x=SqFt))	+	geom_histogram()
p4 <- ggplot(housing,	aes(x=Units))	+	geom_histogram()
grid.arrange(p3, p4, nrow = 1)

```

## Boxplots for predictor variable

```{r}
p5 <- ggplot(housing,	aes(y=SqFt,x=1))	+	geom_boxplot()
p6 <- ggplot(housing,	aes(y=Units,x=1))	+	geom_boxplot()
grid.arrange(p5, p6, nrow = 1)
```

## Finding Outlier Points

```{r}
housing[housing$Units	>	1000,	]

```

## Removing Outlier Points

```{r}
housing <- housing[housing$Units <   1000, ]
```

## Fitting Regression Model

```{r}
house1	<- lm(ValuePerSqFt	~	Units	+	SqFt	+	Boro,	data=housing)
summary(house1)
```

## Getting Model Coefficients

```{r}
coef(house1)
```

## Plotting Coefficients

```{r}
library(coefplot)
coefplot(house1)
```

## Fitting model with interaction terms

```{r}
house2	<- lm(ValuePerSqFt	~	Units	*	SqFt	+	Boro,	data=housing)
house3	<- lm(ValuePerSqFt	~		Units	:	SqFt	+	Boro,	data=housing)
multiplot(house1,	house2,	house3)
```

## Reading in test housing dataset

```{r}
housingNew	<- read.table("../data/housingNew.csv", sep=",",	header=TRUE,	stringsAsFactors=FALSE)
head(housingNew)
```

## Predicting using our regression model

```{r}
housePredict	<- predict(house1,	newdata=housingNew,	se.fit=TRUE,interval="prediction",	level=.95)
#view	predictions	with	upper	and	lower	bounds	based	on	standard	errors
head(housePredict$fit)
```

