---
title: "Reading Data Into R"
author: "Vivekanandan Srinivasan"
date: "9/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading in tomato data from url

```{r }
url <- "http://www.jaredlander.com/data/Tomato%20First.csv"
tomato <- read.table(file = url, header = TRUE, sep = ",")
head(tomato)
dim(tomato)
```

## Reading CSV using readr library

```{r}
library(readr)
theUrl	<- "http://www.jaredlander.com/data/TomatoFirst.csv"
tomato2	<-read_delim(file=theUrl,	delim=',')

```

```{r}
tomato2
```

## Reading csv using fread from data.table

```{r}
library(data.table)
theUrl	<- "http://www.jaredlander.com/data/TomatoFirst.csv"
tomato3	<-fread(input=theUrl,	sep=',',	header=TRUE)

```


## Reading from Excel

```{r}

download.file(url='http://www.jaredlander.com/data/ExcelExample.xlsx',destfile='../data/ExcelExample.xlsx')
```

```{r}
library(readxl)
excel_sheets('../data/ExcelExample.xlsx')

```

## Reading specific sheet from Excel

```{r}
wineXL1	<- read_excel('../data/ExcelExample.xlsx',	sheet=2)
head(wineXL1)

```


## Reading from databases

```{r}
download.file("http://www.jaredlander.com/data/diamonds.db",destfile	=	"../data/diamonds.db",	mode='wb')
```

## Example Using RSQlite

```{r}
library(RSQLite)
```

## Specifying Driver

```{r}
drv	<- dbDriver('SQLite')
class(drv)
```

## Establishing database connection

```{r}
con	<- dbConnect(drv,	'../data/diamonds.db')
class(con)
```

## Listing tables

```{r}
dbListTables(con)
dbListFields(con,	name='diamonds')
```

```{r}

```

## DBQuery

```{r}
longQuery	<- "SELECT	*	FROM	diamonds,	DiamondColors WHERE diamonds.color	=	DiamondColors.Color"
diamondsJoin	<-dbGetQuery(con,	longQuery,stringsAsFactors=FALSE)
head(diamondsJoin)

```



## Example Using RODBC

```{r}
require(RODBC)
# Create a connection to the database called "db"
db <- odbcConnect("DATABASE", uid="USERNAME", pwd="PASSWORD", believeNRows=FALSE)
# Check that connection is working (Optional)
odbcGetInfo(db)
```

## Running simple query in database

```{r}
# Simple SELECT * query from one table
ordersTable <- sqlQuery(db, "SELECT * FROM Orders", stringAsFactors=FALSE)
head(OrderTable)
```


## Joining Two Tables 

```{r}
# Do join between the two tables
query <- "SELECT * FROM Orders, [Order Details] where Orders.OrderID=[Order Details].OrderID
detailsJoin <- sqlQuery(db, query, stringAsFactors=FALSE)
```

## Saving R object to Rdata format



```{r}
save(tomato,file="tomato.rdata")
rm(tomato)
```

## Checking the deleted R object

```{r}
head(tomato)
```

## Reloading tomato data from Rdata

```{r}
load("tomato.rdata")
# Check if it exist now
head(tomato)
```


## Creating Multiple Data

```{r}
n <- 20
r <- 1:10
w <- data.frame(n,r)
head(w)
```

```{r}
save(n,r,w, file="multiple.rdata")
# delete them
rm(n,r,w)

```

```{r}
head(w)
```


```{r}
# now load them back from rdata
load("multiple.rdata")
n
r
```

## Loading data included with R ggplot2


```{r}
require(ggplot2)
data(diamonds)
head(diamonds)
```

## List of all data available in ggplot2 package

```{r}
data()
```

## Scraping table from online resource

```{r}
library(XML)
url <- "http://www.jaredlander.com/2012/02/another-kind-of-super-bowl-pool/"
bowlPool <- readHTMLTable(url, which=1, header=FALSE, stringAsFactors=FALSE)
bowlPool
```

```{r}
library(rvest)
ribalta	<- read_html('http://www.jaredlander.com/data/ribalta.html')
class(ribalta)
ribalta

```


```{r}
ribalta	%>%	html_nodes('.street')	%>%	html_text()

```

```{r}
ribalta	%>%
  html_nodes('table.food-items')	%>%
  magrittr::extract2(5)	%>%
  html_table()
```


## Installing aws.s3 package

```{r}
# latest stable version
install.packages('aws.s3', repos = c('cloudyr' = 'http://cloudyr.github.io/drat'))

# on windows you may need:
#install.packages('aws.s3', repos = c('cloudyr' ='http://cloudyr.github.io/drat'), INSTALL_opts = '--no-multiarch')
```

## Accessing s3 bucket

```{r}
Sys.setenv('AWS_ACCESS_KEY_ID' = '',
           'AWS_SECRET_ACCESS_KEY' = '',
           'AWS_DEFAULT_REGION' = 'us-west-2')

library('aws.s3')
#bucketlist()
# To get listing of all objects in a public bucket
files <- get_bucket(bucket = 'spark-contents')
files
```

## Commonly used function to read and write objects in S3 

```{r}
# save an in-memory R object into S3
s3save(mtcars, bucket = 'my_bucket', object = 'mtcars.Rdata')

# `load()` R objects from the file
s3load('mtcars.Rdata', bucket = 'my_bucket')

# get file as raw vector
get_object('mtcars.Rdata', bucket = 'my_bucket')
# alternative 'S3 URI' syntax:
get_object('s3://my_bucket/mtcars.Rdata')

# save file locally
save_object('mtcars.Rdata', file = 'mtcars.Rdata', bucket = 'my_bucket')

# put local file into S3
put_object(file = 'mtcars.Rdata', object = 'mtcars2.Rdata', bucket = 'my_bucket')
```



