---
title: "Statistical Visualization In R"
author: "Vivekanandan Srinivasan"
date: "9/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading in diamond dataset from ggplot2

```{r}
require(ggplot2)
data(diamonds)
head(diamonds)
```

## Histogram using base graphics

```{r}
hist(diamonds$carat, main="Carat Histogram", xlab="Carat")
```

## Scatterplot with base graphics

```{r}
plot(price ~ carat, data = diamonds)
```

## Scatterplot without using formula

```{r}
plot(diamonds$carat, diamonds$price)
```

## Boxplots with base graphics

```{r}
boxplot(diamonds$carat)
```

## Histogram using ggplot2

```{r}
ggplot(data = diamonds) + geom_histogram(aes(x=carat)) 
```

## Density plot using ggplot2


```{r}
ggplot(data=diamonds) + geom_density(aes(x=carat) , fill = "grey50")
```

## Scatterplot using ggplot2

```{r}
g <- ggplot(diamonds, aes(x=carat,y=price))
g + geom_point(aes(color=color))
```

## Facet_wrap and facet_grid in ggplot2

```{r}
g + geom_point(aes(color=color)) + facet_wrap(~color)
```

```{r}
g + geom_point(aes(color=color)) + facet_grid(cut~clarity)
```

## Boxplot using ggplot2

```{r}
ggplot(diamonds,aes(y=carat,x=1)) + geom_boxplot()
```

```{r}
ggplot(diamonds,aes(y=carat,x=cut)) + geom_boxplot()
```

## Violin Plots using ggplot2

```{r}
require(gridExtra)
p1 <- ggplot(diamonds,aes(y=carat,x=cut)) + geom_point() + geom_violin()
p2 <- ggplot(diamonds,aes(y=carat,x=cut)) + geom_violin() + geom_point()
grid.arrange(p1, p2, ncol=2)
```

## Line plots using ggplot2

```{r}
data(economics)
head(economics)
```

```{r}
ggplot(economics, aes(x=date,y=pop)) + geom_line()
```

## Preparing data for multiple line charts

```{r}
require(lubridate)
## Create month and year columns
economics$year <- year(economics$date)
economics$month <- month(economics$date)
## Subset the data
econ2000 <- economics[which(economics$year>=2000),]
head(econ2000)
```

```{r}
g <- ggplot(econ2000,aes(x=month,y=pop))
g <- g + geom_line(aes(color=factor(year), group=year))
g <- g + scale_color_discrete(name="Year")
g <- g + labs(title="Population Growth", x="Month",y="Population")
g
```

## Theme in ggplot2

```{r}
require(ggthemes)
g2 <- ggplot(diamonds, aes(x=carat,y=price)) + geom_point(aes(color=color))

## Lets apply few themes
p1 <- g2 + theme_economist() + scale_color_economist()
p2 <- g2 + theme_excel() + scale_color_excel()
p3 <- g2 + theme_tufte()
p4 <- g2 + theme_wsj()
grid.arrange(p1, p2, p3, p4, nrow=2, ncol=2)
```

